Instructions for \confname{} Proceedings

### 2019-05-15 papers/EMNLP2019/analysis.tex
updated analysis table, + std, which is huge...

For measuring \textbf{instance-level agreement}, we consider all names annotated for an object as a response set and then average over these response sets. Furthermore, we compute \textbf{category-level agreement} by merging the response sets for all objects that have the same VisualGenome name and compute the measures over these aggregated response sets.
\gbt{I'd call it ``name-level agreement'' -- it's not really category, is it?}
\cs{@Sina (referring to our discussion we've had) object class instead of category would imo be indeed clearer here}

@@

Table \ref{tab:agree} shows the analysis of the instance-level and category-level agreement.
On the instance-level, our annotators achieve a fair amount of overlap in their object naming choices. 
Thus, for roughly 70\% of our objects (\textbf{std=?}), the most frequent response in ManyNames corresponds to the original VisualGenome name and, similarly, the average frequency of the top response is also 70\%. 
Generally, this seems to suggest that indeed many objects in our data set have a canonical name. 
At the same time, the average number of name types per object (5.7, or 2.9 when excluding low-frequency types in each response set) suggests that there is a stable amount of naming variants that is elicited for instances. 
Furthermore, the agreement varies quite considerably among domains \cs{refer to std}:  in the animal domain, which is often discussed in the object naming literature, annotators achieve a very stable and robust agreement of over 90\% and an $H$ agreement which comes close to 0 (where 0 is perfect agreement). 
The people domain, on the other hand, is subject to much more variation and agreement is dramatically lower here, and comes close to 50\% for \% top.

\gbt{Super-interesting results.}
Finally, the category-level agreement figures tell yet another story: when aggregating the responses for all objects with the same VisualGenome name, we obtain on average 28 types (with $N_{>1})$, i.e. 27 variants of the original VG name. 
Surprisingly, here, only 29.4\% of the aggregated response sets still have the VG name as the most frequent response, which means that for 70\% of the VG names, annotators in ManyNames, on average, prefer a different name.  
Likewise, the relative frequency of the top response drops considerably and $H$ increases from 1.3 for instance-level agreement to 2.4 on object-level agreement.  
\cs{Can we say more about what's going on in the people and vehicles domain, category-level, top=VG? E.g., put corresponding examples in Tab.\ref{tab:qual}}
%
\subsection{Discussion (for now)}
What does this discrepancy between the instance-level and category-level agreement in VisualGenome and ManyNames naming choices mean? 
First of all, it suggests that the same original VisualGenome name can trigger very different variants depending on the visual instance, leading to a drastic increase of variants elicited for categories as compared to instances.
Second, this clearly shows that annotators in VG do not generally annotate the most canonical name \cs{but they don't annotate the name, but the description} and that many names annotated for objects in VG do not correspond to the overall most preferred variant. \sz{think more ...}
\gbt{I don't think we can conclude this second part -- we do have the 70\% top=VG figure that says that VG annotators annotate the most canonical name. What this suggests to me is that instance-level properties are more important than category-level properties, somehow.
  That is, there are systematic properties of instances that make them have a single most salient name.
  However, I expect that this result will be very influenced by referential uncertainty (in single images, it will mostly be clear that it's a man, but in some it may be unclear \ra high instance agreement, low category agrement.}
\cs{I don't think that 70\% is high. E.g., the ResNet has a top-1 error rate of 25\% on ILSVRC 2015.}

@@

\begin{table*}
\small
\begin{tabular}{p{1.3cm}ccccccc|ccccccc}
\toprule
 & \multicolumn{7}{c|}{Instance-level agreement} & \multicolumn{7}{c}{Category-level agreement}\\ 
           domain & \% top &    $H$ &    N & N$_{>1}$ & top=VG &  \% VG &      \# Obj & \% top &    $H$ &     N & N$_{>1}$ & top=VG &  \% VG &  \# Cat\\
\midrule
         people &  51.9 &  2.1 &  8.6 &   4.3 &   49.8 &  32.3 &   4533 &  43.8 &  2.9 &  88.5 &  45.1 &   20.0 &  10.9 &   55 \\
         clothing &  63.9 &  1.6 &  6.4 &   3.2 &   70.2 &  52.6 &   2192 &  50.6 &  2.5 &  68.3 &  32.5 &   38.5 &  24.6 &   39 \\
           home &  66.4 &  1.5 &  6.3 &   3.1 &   78.5 &  58.8 &   6292 &  50.7 &  2.7 &  90.6 &  42.6 &   39.3 &  24.9 &   89 \\
      buildings &  66.9 &  1.5 &  6.9 &   3.0 &   72.6 &  55.5 &    967 &  47.8 &  2.9 &  59.9 &  27.2 &   27.8 &  19.2 &   36 \\       
                  food &  71.3 &  1.3 &  5.5 &   2.9 &   62.9 &  52.1 &   1975 &  47.0 &  2.5 &  31.5 &  15.0 &   29.3 &  19.3 &   92 \\
              vehicles &  72.0 &  1.1 &  4.7 &   2.4 &   71.1 &  60.2 &   4552 &  56.5 &  2.0 &  63.3 &  30.0 &   18.4 &  17.9 &   49 \\
        animals,plants &  91.3 &  0.4 &  2.7 &   1.5 &   93.8 &  88.0 &   4804 &  67.6 &  1.5 &  26.5 &  12.3 &   28.1 &  25.7 &   89 \\
       \midrule
       all &  69.7 &  1.3 &  5.7 &   2.9 &   72.8 &  58.7 &  25315 &  52.8 &  2.4 &  58.2 &  27.8 &   29.4 &  20.9 &  449 \\

\bottomrule
\end{tabular}\caption{Agreement in naming measured on the level of instances and on the level of VG categories (i.e.\ after grouping objects by their VG name) \cs{\textbf{std=?})}}
\label{tab:agree}
\end{table*}

>>>>

For measuring \textbf{instance-level agreement}, we consider all names annotated for an object as a response set and then average over these response sets. Furthermore, we compute \textbf{class-level agreement} by merging the response sets for all objects that have the same synset (given for the original VisualGenome name) and compute the measures over these aggregated response sets.
%\gbt{I'd call it ``name-level agreement'' -- it's not really category, is it?}
%\cs{@Sina (referring to our discussion we've had) object class instead of category would imo be indeed clearer here}

@@

Table \ref{tab:agree} shows the analysis of the instance-level and category-level agreement.
On the instance-level, our annotators achieve a fair amount of overlap in their object naming choices. 
Thus, for roughly 70\% of our objects (\textbf{std=?}), the most frequent response in ManyNames corresponds to the original VisualGenome name and, similarly, the average frequency of the top response is also 70\%. 
%Generally, this seems to suggest that indeed many objects in our data set have a canonical name. 
\sz{For NLP people, this looks like a good agreement (given that people were free to type what they wanted). For vision people who might think of it as an object labeling task, this would be pretty low/bad agreement.}
At the same time, the average number of name types per object (5.7, or 2.9 when excluding low-frequency types in each response set) suggests that there is a stable amount of naming variants that is elicited for instances. 
Furthermore, the agreement varies quite considerably among domains \cs{refer to std}:  in the animal domain, which is often discussed in the object naming literature, annotators achieve a very stable and robust agreement of over 90\% and an $H$ agreement which comes close to 0 (where 0 is perfect agreement). 
The people domain, on the other hand, is subject to much more variation and agreement is dramatically lower here, and comes close to 50\% for \% top.

\gbt{Super-interesting results.}
Finally, the category-level agreement figures tell yet another story: when aggregating the responses for all objects with the same VisualGenome synset, we obtain on average 30 types (with $N_{>1})$, i.e. variants of the original VG class. 
Surprisingly, here, only 32.7\% of the aggregated response sets still have the VG name as the most frequent response, which means that for 70\% of the VG names, annotators in ManyNames, on average, prefer a different name.  
Likewise, the relative frequency of the top response drops considerably and $H$ increases from 1.3 for instance-level agreement to 2.4 on object-level agreement.  
\cs{Can we say more about what's going on in the people and vehicles domain, category-level, top=VG? E.g., put corresponding examples in Tab.\ref{tab:qual}}
%
\subsection{Discussion (for now)}
What does this discrepancy between the instance-level and category-level agreement in VisualGenome and ManyNames naming choices mean? 
First of all, it suggests that the same original VisualGenome name can trigger very different variants depending on the visual instance, leading to a drastic increase of variants elicited for categories as compared to instances.
Second, this clearly shows that annotators in VG do not generally annotate the most canonical name \cs{but they don't annotate the name, but the description} and that many names annotated for objects in VG do not correspond to the overall most preferred variant. \sz{think more ...}
\gbt{I don't think we can conclude this second part -- we do have the 70\% top=VG figure that says that VG annotators annotate the most canonical name. What this suggests to me is that instance-level properties are more important than category-level properties, somehow.
  That is, there are systematic properties of instances that make them have a single most salient name.
  However, I expect that this result will be very influenced by referential uncertainty (in single images, it will mostly be clear that it's a man, but in some it may be unclear \ra high instance agreement, low category agrement.}
\cs{I don't think that 70\% is high. E.g., the ResNet has a top-1 error rate of 25\% on ILSVRC 2015.}

@@

\begin{table*}
\footnotesize
\begin{tabular}{p{1.3cm}cccccc|cccccc}
\toprule
 & \multicolumn{6}{c|}{Instance-level agreement} & \multicolumn{6}{c}{Class-level agreement}\\ 
           domain & \% top &    $H$ &    N & N$_{>1}$ & top=VG &  \% VG & \% top &    $H$ &     N & N$_{>1}$ & top=VG &  \% VG \\
\midrule
            all &  69.7 (22.2) &  1.3 &  5.7 &   2.9 &  72.8  &  58.7  &   52.6 (21.1) &  2.4 &   62.2 &  29.7 &  32.7 (46.9) &  23.5 (27.0)  \\
 \midrule
         people &  51.9 (18.1) &  2.1 &  8.6 &   4.3 &         49.8 &         32.3 &     43.1 (14.9) &  2.9 &  104.4 &  53.4 &         24.4 &         13.2  \\
 animals\_plants &  91.3 (12.9) &  0.4 &  2.7 &   1.5 &         93.8 &         88.0 &     67.9 (23.5) &  1.5 &   26.7 &  12.4 &         29.5 &         26.2  \\
       clothing &  63.9 (17.9) &  1.6 &  6.4 &   3.2 &         70.2 &         52.6 &     49.3 (16.6) &  2.6 &   71.7 &  34.1 &         40.5 &         26.1  \\
       vehicles &  72.0 (19.5) &  1.1 &  4.7 &   2.4 &         71.1 &         60.2 &    54.4 (17.4) &  2.1 &   70.4 &  33.2 &         21.4 &         21.3  \\
      buildings &  66.9 (20.5) &  1.5 &  6.9 &   3.0 &         72.6 &         55.5 &      46.7 (18.2) &  3.0 &   68.5 &  31.3 &         32.3 &         22.3  \\
           home &  66.4 (20.5) &  1.5 &  6.3 &   3.1 &         78.5 &         58.8 &     49.6 (18.7) &  2.8 &  103.2 &  48.8 &         45.9 &         30.1  \\
           food &  71.3 (21.1) &  1.3 &  5.5 &   2.9 &         62.9 &         52.1 &     47.3 (19.5) &  2.5 &   32.1 &  15.2 &         31.1 &         20.8  \\
\bottomrule
\end{tabular}\caption{Agreement in naming measured on the level of instances and on the level of VG classes (i.e.\ after grouping objects by their VG synset) \cs{\textbf{std=?})}}
\label{tab:agree}
\end{table*}
